\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation

### 2015-12-23 pdbf-doc.tex
pdbf compiler now correctly supports compressed xref tables (PDF version >= 1.5)
replaced phantom-js for mac with a working version

Version 1.1.2
Converted windows to unix line-endings
Version 1.2.1 - Bugfixes - renamed signatureplot to compareToBest

\title{\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation}
\author{
 Patrick Bender\\
  \texttt{s9pabend@stud.uni-saarland.de}
}
\date{\today{}, Saarbrücken}

@@

\def\a{5cm}
\def\b{10.5cm}

@@

\section{Getting started}
\begin{itemize}
\item Make sure you have a Java Runtime (version $>=$ 1.7) installed
\item \href{https://github.com/uds-datalab/PDBF/archive/gh-pages.zip}{Download the latest version}
\item Extract zip and change workingdir to extracted folder
\item Adjust config.cfg
\item Try to compile pdbf-doc.tex file with this command: \texttt{java -jar pdbf.jar pdbf-doc.tex}
\item Open pdbf-doc.html, this is the final output of the compilation process, if you rename it to ".pdf" it is also a valid pdf-document
\item Optionally you can attach the included vldb-Invaders.ova (Space invaders clone) or \href{https://github.com/uds-datalab/PDBF/releases/download/1.0.1/dsl.ova}{download the dsl.ova} (Damn small linux) VirtualBox image and attach it to the compiled PDBF file with this command: \texttt{java -jar pdbf.jar --vm pdbf-doc.html vldb-Invaders.ova}.
\item Open pdbf-doc.ova, this is the final output with the attached ova file. Its still a valid pdf and html at the same time.
\item You can play around with the minimal.tex file which contains a minimal example of PDBF usage
\item For further information take a look at the \href{http://uds-datalab.github.io/PDBF/}{documentation}
\end{itemize}

@@

\newpage
\section{PDBF elements}
\textbf{Note:} All PDBF elements use the font size, font family, and font style that was active at the point of their definition. You can for example surround all commands with \verb|\textbf{...}|, \verb|\emph{...}| or any other font command.\\[3pt]
\subsection{Chart}
\begin{figure}[h!]%
\hspace{-218pt}Examples:\\
    \centering
    \begin{minipage}{.48\textwidth}
    \chart[width=\textwidth, height=0.6\textwidth, chartType=line]{SELECT * FROM test;}
    \caption{Line Chart}
    \end{minipage}
    \hspace{11pt}
    \begin{minipage}{.48\textwidth}
    \chart[width=\textwidth, height=0.6\textwidth, chartType=bar]{SELECT * FROM test;}
    \caption{Bar Chart}
    \end{minipage} \\[8pt]
    \begin{minipage}{1.0\textwidth}
    \chart[width=\textwidth, height=0.36\textwidth, chartType=signatureplot]{SELECT b FROM test;}
    \caption{Signatureplot Chart}
    \end{minipage}
\end{figure}

@@

\option
{chartType}
{Sets the type of the chart.}
{\texttt{line} or \texttt{bar} or \texttt{signatureplot}}
{\texttt{line}}

>>>>

\title{\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation}
\author{
 Patrick Bender\\
  \texttt{s9pabend@stud.uni-saarland.de}
}
\date{}

@@

\def\a{5cm}
\def\b{11.2cm}

@@

\section{Getting started}
\begin{itemize}
\item Make sure you have a Java Runtime (version $>=$ 1.7) and a LaTeX distribution installed
\item \href{https://github.com/uds-datalab/PDBF/archive/gh-pages.zip}{Download the latest version}
\item Extract zip and change workingdir to extracted folder
\item Adjust config.cfg
\item Try to compile minimal.tex file with this command: \texttt{java -jar pdbf.jar minimal.tex}
\item Open minimal.html, this is the final output of the compilation process, if you rename it to ".pdf" it is also a valid pdf-document
\item Optionally you can attach the included vldb-Invaders.ova (Space invaders clone) or \href{https://github.com/uds-datalab/PDBF/releases/download/1.0.1/dsl.ova}{download the dsl.ova} (Damn small linux) VirtualBox image and attach it to the compiled PDBF file with this command: \texttt{java -jar pdbf.jar --vm minimal.html vldb-Invaders.ova}.
\item Open minimal.ova, this is the final output with the attached ova file. Its still a valid pdf and html at the same time.
\item You can play around with the minimal.tex file. It contains a small example on how to specify PDBF elements in LaTeX
\item For further information take a look at the \href{http://uds-datalab.github.io/PDBF/}{documentation}
\end{itemize}

@@

\newpage
\section{PDBF elements}
\textbf{Note:} All PDBF elements use the font size, font family, and font style that was active at the point of their definition. You can for example surround all commands with \verb|\textbf{...}|, \verb|\emph{...}| or any other font command.\\[3pt]
\subsection{Chart}
\begin{figure}[h!]%
\hspace{-218pt}Examples:\\
    \centering
    \begin{minipage}{.48\textwidth}
    \chart[width=\textwidth, height=0.6\textwidth, chartType=line]{SELECT * FROM test;}
    \caption{Line Chart}
    \end{minipage}
    \hspace{11pt}
    \begin{minipage}{.48\textwidth}
    \chart[width=\textwidth, height=0.6\textwidth, chartType=bar]{SELECT * FROM test;}
    \caption{Bar Chart}
    \end{minipage} \\[8pt]
    \begin{minipage}{1.0\textwidth}
    \chart[width=\textwidth, height=0.36\textwidth, chartType=compareToBest]{SELECT b FROM test;}
    \caption{compareToBest Chart}
    \end{minipage}
\end{figure}

@@

\option
{chartType}
{Sets the type of the chart.}
{\texttt{line} or \texttt{bar} or \texttt{compareToBest}}
{\texttt{line}}

\noindent\textbf{Note:} A chart or multiplot chart with option "chartType" set to "compareToBest" expects either an array of numbers or an array of an array of numbers as input. It plots the slowdown compared to the best value in the array. In the second case the inner array of numbers contains values for repetitions of the same experiment. \\[6pt]
